The \project{UNRAVE} catalog

### 2016-08-15 article/unrave.tex
Add citations

The first \project{Gaia} data release includes positions, proper motions, and 
parallaxes for approximately two million stars in the Tycho-2 catalog \citep{tycho2}.  
After cross-matching all major stellar spectroscopic surveys\footnote{Specifically 
we cross-matched the Tycho-2 catalog against {APOGEE} \citep{apogee}, 
\project{GALAH} \citep{galah}, \project{Gaia-ESO} \citep{ges}, \project{LAMOST}
\citep{lamost}, and \project{RAVE} \citep{rave}}, we found the RAdial Velocity
Experiment (hereafter \rave) 
survey to have the largest overlap with the first \project{Gaia} data release: 
292,036 stars.  We then used the \project{Gaia} universe model \citep{GUMS} to 
estimate the precision in parallax and proper motions that will be available in 
\project{Gaia} DR1 for every star in these cross-matches.  Comparing the 
expected precision to what is currently available, we further found that the 
\project{RAVE} survey will benefit most from \project{Gaia} DR1.  The distances
of 63\% of the \project{RAVE}--\project{Gaia} DR1 overlap sample (182,862 stars)
are expected to improve with the first \project{Gaia} data release, and 47\% of
stars likely to have better proper motions (137,211 stars).  This motivated us to
examine what chemical abundance information is currently available for \rave, and
to evaluate whether we could contribute to this existing set.

@@

As the name implies, the \rave\ survey was principally designed to obtain radial
velocity measurements for up to $10^6$ stars.  Detailed chemical abundances were
a secondary science goal of the survey.  For this reason the distribution
of S/N ratios for \rave\ spectra is considerably lower than stellar 
spectroscopic surveys where chemical abundances are the defining objective.  The 
\rave\ spectra cover $\approx38$~nm in the infrared with an effective resolution
$\mathcal{R} \approx 7500$, and the S/N peaks at $\approx$50~per~pixel$^{-1}$.
For comparison, the \project{GALAH} survey \citep{DaSilva_2015} --- which was 
specifically constructed for detailed chemical abundance analyses --- includes a
wavelength range about 2.5 times larger at resolution $\mathcal{R} \approx 28,000$,
and target for S/N $\gtrsim100$.

Despite the relatively low resolution and S/N of the spectra, the \rave\ data
releases have demonstrated the team's enormous success in deriving radial 
velocities, stellar astrophysical parameters ($\teff$, $\logg$), as well as 
individual chemical abundances \citep{Steinmetz_2006,Zwitter_2008,Siebert_2011,
Kordopatis_2014, Kunder_2016}.  The data used for this analysis are the result
of a thorough reprocessing of all survey data.  This includes a detailed
re-reduction of the original data frames, an updated continuum-normalization
procedure, as well as an improvement on the quantification of flux errors in
each pixel.  At the end of this processing for each survey observation we are 
provided with: wavelengths, continuum-normalized fluxes, as well as 
$1\sigma$ uncertainties in flux values.  We refer the reader to the official 
fifth data release paper of the \rave\ survey, as presented by
\citet{Kunder_2016}, for more details of this reprocessing.

We chose not to re-normalize the spectra, as our tests proved to us that the
normalization procedure outlined in \citet{Kunder_2016} is sufficient for our
analysis.  We re-sampled all spectra onto a common rest-wavelength map.
Depending on the fibre used and stellar radial velocity, the rest-frame wavelength
range varied for each star.  Given that fluxes were unavailable in the edge
pixels for most stars, we excluded pixels outside of the rest wavelength range
$8423.2{\rm \AA} < \lambda < 8777.6{\rm \AA}$.

@@

@@

@@

\begin{figure}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{kordopatis_2014}}
\end{figure}

>>>>

The first \project{Gaia} data release includes positions, proper motions, and 
parallaxes for approximately two million stars in the Tycho-2 catalog \citep{Hog_2000}.  
After cross-matching all major stellar spectroscopic surveys\footnote{Specifically 
we cross-matched the Tycho-2 catalog against {APOGEE} \citep{Zasowski_2013}, 
\project{GALAH} \citep{DeSilva_2015}, \project{Gaia-ESO} \citep{Gilmore_2012,Randich_2013}, \project{LAMOST}
\citep{Cui_2012}, and \project{RAVE} \citep{Steinmetz_2006}}, we found the RAdial Velocity
Experiment (hereafter \rave) 
survey to have the largest overlap with the first \project{Gaia} data release: 
292,036 stars.  We then used the \project{Gaia} universe model \citep{Robin_2012} to 
estimate the precision in parallax and proper motions that will be available in 
\project{Gaia} DR1 for every star in these cross-matches.  Comparing the 
expected precision to what is currently available, we further found that the 
\project{RAVE} survey will benefit most from \project{Gaia} DR1.  The distances
of 63\% of the \project{RAVE}--\project{Gaia} DR1 overlap sample (182,862 stars)
are expected to improve with the first \project{Gaia} data release, and 47\% of
stars likely to have better proper motions (137,211 stars).  This motivated us to
examine what chemical abundance information is currently available for \rave, and
to evaluate whether we could contribute to this existing set.

@@

As the name implies, the \rave\ survey was principally designed to obtain radial
velocity measurements for up to $10^6$ stars.  Detailed chemical abundances were
a secondary science goal of the survey.  For this reason the distribution
of S/N ratios for \rave\ spectra is considerably lower than stellar 
spectroscopic surveys where chemical abundances are the defining objective.  The 
\rave\ spectra cover $\approx38$~nm in the infrared with an effective resolution
$\mathcal{R} \approx 7500$, and the S/N peaks at $\approx$50~per~pixel$^{-1}$.
For comparison, the \project{GALAH} survey \citep{DeSilva_2015} --- which was 
specifically constructed for detailed chemical abundance analyses --- includes a
wavelength range about 2.5 times larger at resolution $\mathcal{R} \approx 28,000$,
and target for S/N $\gtrsim100$.

Despite the relatively low resolution and S/N of the spectra, the \rave\ data
releases have demonstrated the team's enormous success in deriving radial 
velocities, stellar astrophysical parameters ($\teff$, $\logg$), as well as 
individual chemical abundances \citep{Steinmetz_2006,Zwitter_2008,Siebert_2011,
Kordopatis_2013, Kunder_2016}.  The data used for this analysis are the result
of a thorough reprocessing of all survey data.  This includes a detailed
re-reduction of the original data frames, an updated continuum-normalization
procedure, as well as an improvement on the quantification of flux errors in
each pixel.  At the end of this processing for each survey observation we are 
provided with: wavelengths, continuum-normalized fluxes, as well as 
$1\sigma$ uncertainties in flux values.  We refer the reader to the official 
fifth data release paper of the \rave\ survey, as presented by
\citet{Kunder_2016}, for more details of this reprocessing.

We chose not to re-normalize the spectra, as our tests proved to us that the
normalization procedure outlined in \citet{Kunder_2016} is sufficient for our
analysis.  We re-sampled all spectra onto a common rest-wavelength map.
Depending on the fibre used and stellar radial velocity, the rest-frame wavelength
range varied for each star.  Given that fluxes were unavailable in the edge
pixels for most stars, we excluded pixels outside of the rest wavelength range
$8423.2\,{\rm \AA} \le \lambda \le 8777.6\,{\rm \AA}$.

@@

\bibitem[Cui et al.(2012)]{Cui_2012} Cui, X.-Q., Zhao, Y.-H., Chu, Y.-Q., et al.\ 2012, Research in Astronomy and Astrophysics, 12, 1197

\bibitem[De Silva et al.(2015)]{DeSilva_2015} De Silva, G.~M., Freeman, K.~C., Bland-Hawthorn, J., et al.\ 2015, \mnras, 449, 2604

\bibitem[Gilmore et al.(2012)]{Gilmore_2012} Gilmore, G., Randich, S., Asplund, M., et al.\ 2012, The Messenger, 147, 25

\bibitem[H{\o}g et al.(2000)]{Hog_2000} H{\o}g, E., Fabricius, C., Makarov, V.~V., et al.\ 2000, \aap, 355, L27

\bibitem[Kordopatis et al.(2013)]{Kordopatis_2013} Kordopatis, G., Gilmore, G., Steinmetz, M., et al.\ 2013, \aj, 146, 134

\bibitem[Kunder et al.(2016)]{Kunder_2016} Kunder, A., et al.\ 2016, in preparation

\bibitem[Ness et al.(2015)]{Ness_2015} Ness, M., Hogg, D.~W., Rix, H.-W., Ho, A.~Y.~Q., \& Zasowski, G.\ 2015, \apj, 808, 16

\bibitem[Randich et al.(2013)]{Randich_2013} Randich, S., Gilmore, G., \& Gaia-ESO Consortium 2013, The Messenger, 154, 47

\bibitem[Robin et al.(2012)]{Robin_2012} Robin, A.~C., Luri, X., Reyl{\'e}, C., et al.\ 2012, \aap, 543, A100

\bibitem[Siebert et al.(2011)]{Siebert_2011} Siebert, A., Williams, M.~E.~K., Siviero, A., et al.\ 2011, \aj, 141, 187

\bibitem[Steinmetz et al.(2006)]{Steinmetz_2006} Steinmetz, M., Zwitter, T., Siebert, A., et al.\ 2006, \aj, 132, 1645

@@

\bibitem[Zasowski et al.(2013)]{Zasowski_2013} Zasowski, G., Johnson, J.~A., Frinchaboy, P.~M., et al.\ 2013, \aj, 146, 81

\bibitem[Zwitter et al.(2008)]{Zwitter_2008} Zwitter, T., Siebert, A., Munari, U., et al.\ 2008, \aj, 136, 421

@@

\begin{figure}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{Kordopatis_2013}}
\end{figure}
